The NIME of the Title Is Hello

### 2025-01-15 src/main.tex
abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. This uses ``nimeart'', a fork of the ``acmart''
  documentclass with additions for the NIME conference. This
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Presented is a design for an electronically augmented replica of a 16th century
harpsichord interface, in the style of a Trasuntino from 1547. The interface was
designed, fabricated and exhibited in a collaboration between the NEMUS project
at the Università di Bologna and the Museo San Colombano, which hosts the
Tagliavini Collection of playable historical keyboard instruments. The interface
was commissioned as part of an exhibition and as a means of interacting with
items in the collection that are no longer in playing condition. The keyboard is
a replica of the mechanism found in harpsichords in the Trasuntino style, with
un-pitched strings under tension to provide a comparable mechanical resistance
as found on an original. A system of infra-red LED / phototransistor pairs were
connected to a microcontroller and  installed inside the interface from which a
stream of data can be generated for each jack. The paper covers the design
criteria, process, open-source development and execution of installation for
exhibition at San Colombano.
\end{abstract}
